---
title: "Grey Literatre Search on Multiple Websites with KagiClient"
author: "Rainer Krug"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: show
    df-print: paged
execute:
  echo: true
  warning: false
  message: false
editor: visual
---

# Setup

```{r}
#| label: setup

devtools::load_all()
# library(rkagi)
```

# Methods

## Define Connection Object


```{r}
#| label: define-connection-object

conn <- new_kagi_connection(
  endpoint = "search",
  api_key = function() {
    keyring::key_get("API_kagi")
  }
)
```
## Search

### Define Search Objects

```{r}
#| label: define-search-objects

domains <- c(
  "worldbank.org",
  "fao.org",
  "ipbes.net",
  "arxiv.org",
  "researchgate.net",
  "biorxiv.org",
  "osf.io",
  "zenodo.org"
)

query <- "biodiversity"

queries <- build_kagi_query(
  q = query,
  filetype = c("pdf", "docx"),
  site = domains,
  inurl = NULL,
  intitle = NULL
)

searches <- lapply(
  queries,
  function(q) {
    new_kagi_search(
      conn,
      q,
      limit = 100
    )
  }
)

```

### Perform Searches

```{r}
#| label: perform-search

search_results <- lapply(
  searches,
  function(s) {
    message("Performing search for query: ", s$q)
    res <- kagi_perform(s)
    message("    Search completed with ", res$data |> nrow(), " hits.")
    return(res)
  }
)
```

### Combine Search Results

```{r}
#| label: combine-search-results

search_result <- dplyr::bind_rows(
  lapply(
    search_results,
    function(x) {
      x$data
    }
  )
)
```

## Enrich 

### Define Enrich Objects

```{r}
#| label: define-enrich-objects

enrichments <- lapply(
  query,
  function(x) {
    new_kagi_enrich(
      conn = conn,
      q = x,
      limit = 100
    )
  }
)
```

### Perform Enrichment


```{r}
#| label: perform-enrichment

enrich_results <- lapply(
  enrichments,
  function(s) {
    message("Performing enrichment for query: ", s$q)
    res <- kagi_perform(s)
    message("    Enrichment completed with ", res$data |> nrow(), " hits.")
    return(res)
  }
)
```


### Combine Enrich Results

```{r}
#| label: combine-enrich-results

enrich_result <- dplyr::bind_rows(
  lapply(
    enrich_results,
    function(x) {
      x$data
    }
  )
)
```


## Summarize Search Results

### Define Summarize Objects for Search

```{r}
#| label: define-summarize-search-objects

search_summaries <- lapply(
  search_result$url,
  function(x) {
    new_kagi_summarize(
      conn = conn,
      url = x,
      text = NULL,
      engine = "cecil",
      summary_type = "summary",
      target_language = "EN"
    )
  }
)
```

### Perform Summarization of Search

```{r}
#| label: perform-search-summarization

summarize_serach_results <- lapply(
  search_summaries,
  function(s) {
    message("Performing summarization for url: ", s$URL)
    res <- kagi_perform(s)
    message("    Summarization completed.")
    return(res)
  }
)
```


## Summarize Enrich Results

### Define Summarize Objects for Enrich

```{r}
#| label: define-summarize-enrich-objects

search_summaries <- lapply(
  enrich_result$url,
  function(x) {
    new_kagi_summarize(
      conn = conn,
      url = x,
      text = NULL,
      engine = "cecil",
      summary_type = "summary",
      target_language = "EN"
    )
  }
)
```

### Perform Summarization of Enrichment

```{r}
#| label: perform-enrich-summarization

summarize_serach_results <- lapply(
  enrich_summaries,
  function(s) {
    message("Performing summarization for url: ", s$URL)
    res <- kagi_perform(s)
    message("    Summarization completed.")
    return(res)
  }
)
```


# Results

## Search Results

```{r}
#| label: search-results

search_result |>
  knitr::kable()
```

## Enrich Results

```{r}
#| label: enrich-results

enrich_result |>
  knitr::kable()
```
